---
title: "STAT545 Notebook"
date: 11/06/2018
output: 
  github_document:
    toc: true
    toc_depth: 2
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, # knitr will put the source and output blocks in a single block
  comment = "#>",
  fig.path = "README-"
)
```


### 1. Basic Working of RStudio
* **The assign operator `<-`**  
The operator `<-` is recommended to use when coding. A shortcut to input the operator is __Alt+-__. RStudio automatically surrounds it with spaces.

* **Keyboard shortcuts**  
Try __Alt+Shift+K__ to see the list of shortcuts in RStudio.

* **R chunk**  
    * insert a R chunk: __Ctrl+Alt+I__.
    * run a R chunk: placing the cursor inside it and pressing __Ctrl+Shift+Enter__.

* **Clear Environment tab**  
`ls()` gives the whole stuff stored in the environment at the moment  
Clear the workspace to ensure the code is re-runnable:
```{r}
ls()
rm(list = ls())
```

* **Dataframe**
    * use the package `tidyverse`, which includes popular packages like `dplyr` and `ggplot2`.
    * matrix has a homogenous structure, which means we can't put character data into a numeric matrix.
    * `data()` gives the full list of the datasets of loaded packages

### 2. dplyr functions

* **`mutate()` function**  
To get rid of a new variable by setting it to `NULL`.
```{r}
mtcars %>% head(10) %>%
  mutate(tmp1 = wt * 10, tmp2 = qsec * 10, tmp1 = NULL)

```

* **`rename()` function  **  
To chage column names by using `rename()`.
```{r}
mtcars[, 1:5] %>% head(10) %>%
  rename(mpg.NEW = mpg,
         cyl.NEW = cyl,
         disp.NEW = disp)
```

* **`select()` function**  
    - `select()` can change the name of columns request to keep.
    - `everthing()` selects all columns.
```{r}
mtcars[, 1:5] %>% head(10) %>%
  select(mpg.NEW = mpg, everything())
```

* **`tally()` function**  
    - A convenience function that knows to count rows.
    - `count()` gives the same result.
```{r}
mtcars %>% group_by(gear) %>%
  tally()

mtcars %>% count(gear)
```

* **`summarise_at()` function**  
    - applies the summarise function(s) to multiple variables
```{r}
mtcars %>%
  group_by(cyl) %>%
  summarise_at(vars(mpg, disp, hp), funs(mean, median))
```
    
* **`first()`, `last()`, `nth()`**  
Extract the first, last or nth value from a vector.  
It doesn't collapse the *n* rows for each group into one row, but compute within them.  
```{r}
mtcars[, 1:5] %>%
  group_by(cyl) %>%
  mutate(qsec.diff = disp - first(disp))
```

* **`min_rank()` function**  
`min_rank()` is a windowed function, taking *n* inputs and giving back *n* outputs.  
Compared with `rank` and `order`, `min_rank()` is the one having the right result. Since `mtcars` is grouped by `cyl`, `min_rank()` operates within the subset. 
```{r}
mtcars[, 1:5] %>%
  group_by(cyl) %>%
  filter(min_rank(hp) == 1)

mtcars[, 1:5] %>%
  group_by(cyl) %>%
  filter(rank(hp) == 1)

mtcars[, 1:5] %>%
  group_by(cyl) %>%
  filter(order(hp) == 1)
```

* **`top_n()` function**  
Select top (or bottom) n rows by value. The wrapper of `filter()` and `min_rank()` has the same result.  
`min_rank()` orders the vector from the smallest. `top_n()` orders the vector from the largest. Use a negative `-` to revert the order.
```{r}
mtcars %>%
  filter(min_rank(hp) <= 3)

mtcars %>%
  top_n(-3, hp)
```





























