---
title: "STAT545 Notebook"
output: 
  github_document:
    toc: true
    toc_depth: 2
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


## 1. Basic Working of RStudio
`Date: 11/06/2018`

#### 1.1 The operator `<-`
The operator `<-` is recommended to use when coding. A shortcut to input the operator is __Alt+-__. RStudio automatically surrounds it with spaces.

#### 1.2 Keyboard shortcuts
Try __Alt+Shift+K__ to see the list of shortcuts in RStudio.

#### 1.3 R chunk
  * insert a R chunk: __Ctrl+Alt+I__.
  * run a R chunk: placing the cursor inside it and pressing __Ctrl+Shift+Enter__.

#### 1.4 Clear Environment tab
`ls()` gives the whole stuff stored in the environment at the moment
```{r}
ls()
```

Clear the workspace to ensure the code is re-runnable:
```{r}
rm(list = ls())
```

#### 1.5 Dataframe
  * use the package `tidyverse`, which includes popular packages like `dplyr` and `ggplot2`.
  * matrix has a homogenous structure, which means we can't put character data into a numeric matrix.
  * `data()` gives the full list of the datasets of loaded packages

## 2. dplyr functions

#### 2.1 `mutate()` function
To get rid of a new variable by setting it to `NULL`.

```{r}
mtcars %>% head(10) %>%
  mutate(tmp1 = wt * 10, tmp2 = qsec * 10, tmp1 = NULL)

```



































